(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-06 ms.tex
more FPP text

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new implementation of the \citet{Morton12} procedure, to calculate
the false positive probabilities of each of these K2 candidates.  
While we do have follow-up observations of a number of these systems,
we do the preliminary FPP calculations without taking these into account,
relying solely on the probabilistic \texttt{vespa} analysis.

@@

We find that \Nfp\ of the presented candidates have false positive
probabilities (FPPs) $>$90\%; these we consider to be likely false
positives.  
On the other hand, we find that \Nvalidated\ candidates
have FPP $<$ 1\%; these we consider to be validated planets.  
The remaining \Nlimbo\ candidates have FPPs neither high enough to discard
nor low enough to securely validate.

>>>>

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new implementation of the \citet{Morton12} procedure, to calculate
false positive probabilities (FPPs) for each of these K2 candidates.  
While we have obtained follow-up observations of a number of these systems,
we do the preliminary FPP calculations without taking these into account,
in order to demonstrate the power of \texttt{vespa} analysis
even in the absence of follow-up observations.  
The constraints we impose on false positive scenarios in these
``follow-up free'' calculations are the following:
\begin{itemize}
\item A chance-aligned eclipsing binary system must reside within 
a 4 arcsecond radius of the target star.
\item The maximum allowed depth of a potential secondary eclipse event,
determined as the most significantly detected signal at the same 
period of the planet candidate, once the primary transit is masked out.
\end{itemize}

@@

We find that \Nfp\ of the presented candidates FPP $>$90\%; 
these we consider to be likely false positives.  
On the other hand, we find that \Nvalidated\ candidates
have FPP $<$ 1\%; these we consider to be validated planets.  
The remaining \Nlimbo\ candidates have FPPs neither high enough to discard
nor low enough to securely validate.
